Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Typos and missing words.

Verified systems have been growing in popularity recently with the rise of proof
assistants like Coq and NuPRL~\cite{coqart,nuprl}.  These systems allow
programmers to construct proofs of properties of their programs which are
checked and compiled by the system.  As we will discuss in
Section~\ref{sec:related}, these \emph{Proof Assistants} have been used to
formalize, prove correct, and implement systems with verified properties.  This
increases programmers' confidence in their languages and programs; to prove
correctness of a function is a much stronger guarantee than simply testing
functionality (or asserting correctness in the absence of tests).

@@

Given the growing popularity of Proof Assistants information-flow languages, we
were surprised to discover that there has not been work done to formalize ad
verify a language with a type system which enforces information flow security
policies.  These languages seem a natural choice for formal verification, as it
is desirable for programs written in these languages to be accompanied with a
proof of the security properties they enforce.  Our goal is to make progress
towards verifying the correctness of a compiler for a language with information
flow types that programmers will want to use.

@@

    As seen in Figure~\ref{fig:syntax}, we have a slightly different syntax
    structure for \langName than was seen in~ \origLang.  Specifically, we
    constructed values, answers, and expressions explicitly to not allow nesting
    of bracketed values.  The syntax defined by Simonet and Pottier did allow
    for this nesting, and authors dismissed is as a non-sensible construction.
    Unfortunately, allowing such syntactic nesting prevents the completeness
    Lemma from being proveable.  Realizing that our definitions did not disallow
    this by construction after running into issues in the proof, we were able to
    fix the definition, producing what is in Figure~\ref{fig:syntax}.

@@

Once our noninterference proof has been sucessfully mechanized for \langName, we
will incrementally enhance the features of \langName, adding in absent
constructs such as bind, references, and exceptions.  We will then re-state and
re-prove the noninterference result in a language very much like \origLang.

>>>>

Verified systems have been growing in popularity recently with the rise of proof
assistants like Coq and NuPRL~\cite{coqart,nuprl}.  These systems allow
programmers to construct proofs of properties of their programs which are
checked and compiled by the system.  As we will discuss in
Section~\ref{sec:related}, these \emph{proof assistants} have been used to
formalize, prove correct, and implement systems with verified properties.  This
increases programmers' confidence in their languages and programs; to prove
correctness of a function is a much stronger guarantee than simply testing
functionality (or asserting correctness in the absence of tests).

@@

Given the growing popularity of proof assistants and information-flow languages,
we were surprised to discover that there has not been work done to formalize ad
verify a language with a type system which enforces information flow security
policies.  These languages seem a natural choice for formal verification, as it
is desirable for programs written in these languages to be accompanied with a
proof of the security properties they enforce.  Our goal is to make progress
towards verifying the correctness of a compiler for a language with information
flow types that programmers will want to use.

@@

    As seen in Figure~\ref{fig:syntax}, we have a slightly different syntax
    structure for \langName than was seen in~ \origLang.  Specifically, we
    constructed values, answers, and expressions explicitly to not allow nesting
    of bracketed values.  The syntax defined by Simonet and Pottier did allow
    for this nesting, and authors dismissed is as a non-sensible construction.
    Unfortunately, allowing such syntactic nesting prevents the completeness
    Lemma from being provable.  Realizing that our definitions did not disallow
    this by construction after running into issues in the proof, we were able to
    fix the definition, producing what is in Figure~\ref{fig:syntax}.

@@

Once our noninterference proof has been successfully mechanized for \langName,
we will incrementally enhance the features of \langName, adding in absent
constructs such as bind, references, and exceptions.  We will then re-state and
re-prove the noninterference result in a language very much like \origLang.
